---
title: "ggplot_hook"
author: "Dang Nhat"
date: "2022-12-22"
output: pdf_document
---


```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```


## Setting up my enviroment
Notes: setting up my R enviroment by loading packages:
* tydyverse
* palmerpenguins

```{r loading packages}
library(tidyverse)
library(palmerpenguins)
```

## Visualizations
Here we will go through a series of visualizations

### Flipper and body mass in purple
Here, we pot flipper length against body mass
```{r visualize flipper and body mass in purple}
penguins %>% 
  ggplot() + geom_point(aes(x=flipper_length_mm, y=body_mass_g, color="purple"))

```

### Flipper and body mass by species
Here, we plot flipper length against body mass and look at the breakdown by species

```{r species}
penguins %>% 
  ggplot() + geom_point(aes(x=flipper_length_mm, y=body_mass_g, color="purple", shape=species))

```

### Flipper and body mass by species and sex
Here, we plot flipper length against body mass and look at the breakdown by species and sex

```{r species and sex}
penguins %>% 
  ggplot() + geom_point(aes(x=flipper_length_mm, y=body_mass_g, color=species, shape=species))+
  facet_wrap(~sex)

```

